\documentclass[11pt]{revtex4-1}
\usepackage{amsmath}
\begin{document}

\subsection*{Q: Can cmd:text used inside paragraph mode?}
Test: \text{hello} \\
A: Yes

\subsection*{Q: Is the font in cmd:text forced to be roman? Or just use the same font with outer env?}
Test \textit{hello \text{small} world} \\
A: Use outer font

\subsection*{Q: What is the font in math-mode cmd:text?}
Test: \texttt{ABC $DEF \text{GHI} JKL$ MNO}
A: The font of outside paragraph-mode.

\subsection*{Q: How do cmd:emph and cmd:em toggle?}
Test: This {\em hello {\em check test} world} that. \\
Test: {\it This {\em hello {\em check test} world} that}. \\
A: Toggles between rm and it.

\subsection*{Q: Are cmd:emph and cmd:em available in math mode?}
Test: $\emph{Hello \emph{World}}$ \\
%%Test: $\emph{Hello \frac12\emph{World}}$ %% Error
%%Test: $\em Hello \em World$ %% Error
A: cmd:emph Yes, and it turns into paragraph mode as is cmd:text \\
A: cmd:em No

\subsection*{Q: Do cmd:emph and cmd:em remember outer font?}
Test: $\text{A\emph{B}C}$ \\
Test: $\emph{AAA}$ \\
Test: {\it $\text{A\emph{B}C}$ } \\
Test: {\it $\emph{AAA}$} \\
A: Yes

\subsection*{Q: How do cmd:emph and cmd:em behave for other outer fonts?}
Test: {\sf Hello {\em world {\em test}}} \\
Test: {\tt Hello {\em world {\em test}}} \\
Test: {\bf Hello {\em world {\em test}}} \\
Test: slshape {\sl Hello {\em world {\em test}}} \\
Test: scshape {\sc Hello {\em world {\em test}}} \\
Test: itshape {\it Hello {\em world {\em test}}} \\
Test: upshape {\upshape Hello {\em world {\em test}}} \\
A: toggle between ({\sf cmd:sf}, {\sf\em cmd:??}), ({\tt cmd:tt}, {\tt\em cmd:??}), ({\bf cmd:tt}, {\bf\em cmd:??}) \\
A: $sl \to rm \to it$

Test: {\tt Hello \slshape world \upshape world \scshape world \itshape world} \\
Test: {\rm Hello \bfseries world \mdseries world} \\
Conclusion: It seems that a font is specified by the combination of family, series and shape.
  cmd:em and cmd:emph changes the shape preserving other values.

\subsection*{Q: Does math-mode font-family affect?}
Test: $\mathsf{Hi,how are you? \text{Good!}}$ \\
Test: $\mathsf{Hi,how are you? \text{Good!}}$ \\
A: Yes

%%-----------------------------------------------------------------------------
\section{Test font specification}
\subsection*{Does cmd:ttfamily change the other properties?}
Test: {\bfseries Hello \ttfamily World \rmfamily Test}; {\slshape Hello \ttfamily World}; {\itshape Hello \ttfamily World} \\
A: No. It preserves other properties

\subsection*{Does cmd:tt change the other properties?}
Test: {\bfseries Hello \tt World \rmfamily Test}; {\slshape Hello \tt World}; {\itshape Hello \tt World} \\
A: Yes. It clears.

\subsection*{Does cmd:texttt change the other properties?}
Test: {\bfseries Hello \texttt{World \rmfamily Test}}; {\slshape Hello \texttt{World}}; {\itshape Hello \texttt{World}} \\
A: No. It preserves other properties.

%%-----------------------------------------------------------------------------
\section{Math mode fonts}
\subsection*{Q: Is there cmd:math}
Test: Error %%\math{Hello} \\
Test: Error %%$\math{Hello}$ \\
A: No.

\subsection*{Q: Is math mode font preserved through cmd:text?}
\begin{align}
  \mathbf{Hello = \text{World $Math$}}, \\
  %%\mathbf{Hello = \text{World \mathtt{Math}}}, \\
\end{align}
A: No

\subsection*{Q: Is font(family,series,shape) combination available in math moded?}
\begin{align}
  World,\mathtt{World,\mathbf{World,\mathtt{World}}}
\end{align}
A: No

\end{document}
